GA-based Training-Free NAS Algorithm with Hybrid Score Function

### 2023-05-31 paper/main.tex
update related work part2

    % conclusion
    \subsection{Search Algorithm}

>>>>

    % conclusion
    \subsection{Search Algorithm}
    First assume that input data $D$ are separated into two subset, $D_r$ and $D_t$. Further more, 
    assume $\mathcal F_A$ is the accuracy function, $\mathcal F_S$ the score function, $A_s$ the 
    search algorithm of NAS, and $\mathcal A_L$ the learning algorithm. Then, NAS problem can be 
    described as an optimization problem as follows: 
    \begin{equation}
        \label{equ:nas}
        \mathbb N^*=\max_{\mathbb N^b\in\mathbb N}\mathcal F_A(\mathcal A_L(\mathbb N^b, D_r), D_t)
    \end{equation}
    where $\mathbb N$ is a set of neural architectures, namely, the search space of NAS. 
    For non-training-free NAS 
    \begin{equation}
        \label{equ:non-training_free_nas}
        \mathbb N^b=\mathcal A_S(\mathcal F_A(\mathcal A_L(\mathbb N^s, D_r), D_t), \mathbb N)
    \end{equation}
    and for training-free NAS 
    \begin{equation}
        \label{equ:training_free_nas}
        \mathbb N^b=\mathcal A_S(\mathcal F_S(\mathbb N^s, D_r), \mathbb N)
    \end{equation}
    It can be seen that training-free NAS is comprised of two part, search algorithm $A_S$ and score 
    function $F_S$. 
    There are several search algorithms applied on NAS, including random search, bayesian optimization, 
    reinforcement learning, differentiable search algorithm, metaheuristic algorithm, and hybrid 
    heuristic algorithm. 
    In \cite{https://doi.org/10.48550/arxiv.2006.04647} \cite{Lopes_2021}, random search is applied on. 
    The advantage of random search is simple, easy to implement, and the result can be token as a 
    baseline to more comprehensive search algorithm.

    In \cite{10092788}, search economic (SE) \cite{7379579} is applied on.
